% !TeX root = ../../thesis.tex
\chapter*{Acknowledgements}
I would like to express my heartfelt gratitude to all the people who have accompanied me on this journey.

First of all, to the members of the Theory of Unbound Electrons group at KU Leuven—Anthuan, Cansu, Charlotte, Florian, Maristella, Simen—thank you for the camaraderie, the stimulating conversations, and for making the office a place of both scientific discovery and genuine connection. It was an honour to work alongside you. To Prof. Thomas Jagau, thank you for being such an engaged and inspiring mentor—your enthusiasm and guidance were invaluable.

A very special thank you to Robin, whose mentorship was instrumental throughout this project. Your clarity, patience, and insightful discussions helped me find solid footing in unfamiliar terrain. You made complex problems feel approachable.

To my fellow KU Leuven TCCM classmates—Albert, Steff, Steff 2, Arya, Pauline, Tomas, Bilge, Alaina, Yi Fan—thank you for being such a vibrant and diverse group of individuals. From classroom struggles to international dinners, you made this experience richer. Thank you, Janko, for sharing both good times and the bittersweet ordeal of supporting Bar\c{c}a. I'm sure our paths will cross again, and I look forward to it. 

To the Earls of Leuven, thank you for welcoming me into the fold, on the pitch and in the pub, we shared many laughs and unforgettable memories.

To everyone in the Quantum Chemistry division, thank you for the great coffee breaks, inspiring lectures, and spirited ChemCafés. You created a warm and stimulating academic environment that I'll always treasure.

A sincere thank you to the TCCM consortium for organising this master's programme. It has been an eye-opening, enriching experience—one that broadened my horizons, introduced me to wonderful people, and gave me stories I'll carry for years to come. I am deeply grateful to `Fundaci{\'o} ``La Caixa''' for the scholarship that made all this possible. Your support granted me an opportunity that I will always value.

To Steff, Olivia, and Shenrui—thank you for being fantastic flatmates and turning a shared space into a home.

Finally, to my family and friends, thank you for your unwavering support, love, and patience. Your belief in me gave me strength through the ups and downs.

\iffalse Thank you to my family for supporting me through this process, I hope I can make you proud.
Thank you to my friends for being there for me, I hope we can continue to be friends in the future.
Thank you to my girlfriend for being there for me, I hope we can continue to be together in the future.
Thank you to my parents for supporting me through this process, I hope I can make you proud.
Thank you to my brother for being there for me, I hope we can continue to be brothers in the future.
Thank you to my sister for being there for me, I hope we can continue to be siblings in the future.
Thank you to my grandparents for being there for me, I hope we can continue to be family in the future.
Thank you to my aunts and uncles for being there for me, I hope we can continue to be family in the future.
Thank you to my cousins for being there for me, I hope we can continue to be family in the future.
Thank you to my friends for being there for me, I hope we can continue to be friends in the future.
Thank you to my colleagues for being there for me, I hope we can continue to be colleagues in the future.
Thank you to my mentors for being there for me, I hope we can continue to be mentors in the future.
Thank you to my teachers for being there for me, I hope we can continue to be teachers in the future.
Thank you to my professors for being there for me, I hope we can continue to be professors in the future.
Thank you to my advisors for being there for me, I hope we can continue to be advisors in the future.
Thank you to my supervisors for being there for me, I hope we can continue to be supervisors in the future.
Thank you to my friends for being there for me, I hope we can continue to be friends in the future.
Thank you to my family for being there for me, I hope we can continue to be family in the future. \fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file, 
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
